How to select predictive models for decision-making or causal inference?

### 2023-12-17 how_to_select_causal_models.tex
iter

We test model selection across different candidate estimators that
approximate imperfectly the
data-generating process. To build such estimators, we first use a RBF
expansion similar to the one used for data generation. We choose two random
knots and apply a transformation of the raw data features with a Gaussian
kernel. This step is referred as the featurization. Then, we fit a linear
regression on these transformed features. We consider two ways of combining
these steps for outcome mode; we use common nomenclature
\cite{kunzel_metalearners_2019,shen2023rctrep} to refer to these different
meta-learners that differ on how they model, jointly or not, the treated and the
non treated:
\begin{itemize}
    \item SLearner: A single learner for both population, taking the treatment as
          a supplementary covariate.
    \item SftLearner: A single set of basis functions is sampled at random for both
          populations, leading to a given feature space used to model both the treated and
          controls, then two
          separate different regressors are fitted on this shared representation.
    \item TLearner: Two completely different learners for each population, hence
          separate feature representations and regressors.
\end{itemize}

>>>>

We test model selection across different candidate estimators that
approximate imperfectly the
data-generating process. To build such estimators, we first use a RBF
expansion similar to that used for data generation. We choose two random
knots and transform the raw data features with a Gaussian
kernel. This step is referred as the featurization. Then, we fit a linear
regression on these transformed features. We consider two ways of combining
these steps for outcome model; we use common nomenclature
\cite{kunzel_metalearners_2019,shen2023rctrep} to refer to these different
meta-learners that differ on how they model, jointly or not, the treated and the
non treated:
\begin{itemize}
    \item SLearner: A single learner for both population, taking the treatment as
          a supplementary covariate.
    \item SftLearner: A single set of basis functions is sampled at random for both
          populations, leading to a given feature space used to model both the treated and
          controls, then two
          separate different regressors are fitted on this shared representation.
    \item TLearner: Two completely different learners for each population, hence
          separate feature representations and regressors.
\end{itemize}
